Case for Support

### 2021-11-17 application/backgroundToTheResource.tex
Inserted references to Toms citations; fone

At present, progress in the field is held back by the challenge of designing and implementing new experimental protocols, and the difficulty of integrating state-of-the-art data processing and neuroinformatics into custom experimental designs.
%
\textbf{Reproducibility}, in particular, depends on the availability of
standardised tools for experimental control and analysis, shared between
laboratories \citep{baker16,ioannidis05}. Although such tools exist in genetics, astronomy, physics and medicine (Fish et al., 2016; Abdalla et al., 2018, CERN Education, Communications and Outreach Group, 2018, Dickinson et al., 2016, Bycroft et al., 2018), they are mostly lacking in neuroscience, with documented consequences for the reliability of ``discoveries'' (Baker, 2016; Botvinik-Nezer et al., 2020; Button et al., 2013).

>>>>

At present, progress in the field is held back by the challenge of designing and implementing new experimental protocols, and the difficulty of integrating state-of-the-art data processing and neuroinformatics into custom experimental designs.
%
\textbf{Reproducibility}, in particular, depends on the availability of
standardised tools for experimental control and analysis, shared between
laboratories \citep{baker16,ioannidis05}. Although such tools exist in
genetics, astronomy, physics and medicine 
\citep{fishEtAl16,abdallaEtAl18,cern18,dickinsonEtAl16,bycroftEtAl18}, they are
mostly lacking in neuroscience, with documented consequences for the
reliability of ``discoveries'' \citep{baker16,botvinikNezerEtAl20,buttonEtAl13}.
